Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
Some figs larger

\begin{figure}[tb]
  \centering
  \includegraphics[width=1\columnwidth] {images/success-rates-large}
  \caption{Success rates on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
  \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size}
    \caption{Relative makespans of heuristics normalized by \heft makespan, by workflow
    size, on default cluster. Smaller is better.}
    \label{fig:ms-relations-by-workflow}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal}
    \caption{Memory usage on default cluster, including invalid \heft schedules. }
%by algorithm by workflow size
     \label{fig:mem-usages-normal}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal-onlyvalid}
    \caption{Memory usage on default cluster, considering only valid \heft schedules. }
    \label{fig:mem-usages-onlyvalid}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size-constrained}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-constrained-onlyvalid}
    \caption{Memory usage on the memory-constrained  cluster. } % by different heuristics by workflow size.}
    \label{fig:memory-usage-constrained}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/runtimes-logarithmic}
    \caption{Average running times (in seconds) of the heuristics \wrt workflow size. The $y$-axis is logarithmic.}
    \label{fig:runtimes-log}
    \vspace{-0.3cm}
\end{figure}

>>>>

\begin{figure}[tb]
  \centering
  \includegraphics[width=1.08\columnwidth] {images/success-rates-large2}
  \vspace{-0.8cm}
  \caption{Success rates on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
  \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
  \includegraphics[width=1\columnwidth] {images/makespan_relations_by_wf_size2}
    \vspace{-0.8cm}
    \caption{Relative makespans of heuristics normalized by \heft makespan, by workflow
    size, on default cluster. Smaller is better.}
    \label{fig:ms-relations-by-workflow}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-normal2}
    \caption{Memory usage on default cluster, including invalid \heft schedules. }
%by algorithm by workflow size
     \label{fig:mem-usages-normal}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-normal-onlyvalid2}
    \caption{Memory usage on default cluster, considering only valid \heft schedules. }
    \label{fig:mem-usages-onlyvalid}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/makespan_relations_by_wf_size-constrained2}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-constrained-onlyvalid2}
    \caption{Memory usage on the memory-constrained  cluster. } % by different heuristics by workflow size.}
    \label{fig:memory-usage-constrained}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/runtimes-logarithmic2}
    \caption{Average running times (in seconds) of the heuristics \wrt workflow size. The $y$-axis is logarithmic.}
    \label{fig:runtimes-log}
    \vspace{-0.3cm}
\end{figure}
